---
title: "Pitch for Elsevier Subscription cost calculator"
author: "Joonas Siivonen"
date: "8/3/2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction - Open science

- The Finnish Open Science and Research Initiative (ATT) collected the publisher costs 2016.
- Displaying this information and the increase in cost in interactivly increases knowledge on the high subscription costs more efficiently than static plots.
- The data product can be placed for example univeristy library web site 
- The increased knowledge will help with negotiations with the publishers and make a move towards open access


## Engaging design

- User is able to use slider to select year to which predict the costs 
- The predicted values are highlighted and compared to 2010 level to give some scale to the values 
- The webapp is very simple to use but instructions are provided on the page to support novice users. 


## Algorithm

```{r }

```

## Thank you



