---
title: "Pitch for Elsevier Subscription cost calculator"
author: "Joonas Siivonen"
date: "8/3/2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
```

## Introduction - Open science

- The Finnish Open Science and Research Initiative (ATT) collected the publisher costs 2016.
- Displaying this information and the increase in cost in interactivly increases knowledge on the high subscription costs more efficiently than static plots.
- The data product can be placed for example univeristy library web site 
- The increased knowledge will help with negotiations with the publishers and make a move towards open access


## Engaging design

- User is able to use slider to select year to which predict the costs 
- The predicted values are highlighted and compared to 2010 level to give some scale to the values 
- The webapp is very simple to use but instructions are provided on the page to support novice users. 
- [The app](https://sipismi.shinyapps.io/PublicationCosts/)

## Algorithm
Very simple linear regression algorithm is used example code given bellow (evaluated on next slide)
```{r, echo=TRUE, eval=FALSE,tidy=TRUE  }
costs <- read.csv("Publisher_Costs_FI_Full_Data.csv")

#User inputs (deafult values)
uni <- "Aalto University"
year <- "2050"
costs <- filter(costs, Publisher.Supplier == "Elsevier") %>% filter(X...Organization.name == uni)

#building prediction model
model.i <- lm(Cost~Year, costs)
#makin prediction
y <- predict(model.i, data.frame(Year = year))
#add prediction to values
yearlyCosts <- c(costs$Cost, y)
#create vector to color the predicted bar differently 
colours <- c(rep("gray", length(costs$Cost)), "red")
#Create plot
barplot(yearlyCosts, names.arg = c(costs$Year, year) , col = colours, xlab = "Year", ylab="Subscription Cost (EUR)")

#Text output
z <- y/costs$Cost[1]
paste(uni, "will pay", signif(y, digits = 4), "EUR at",year, ".", "This is", round(z, digits=2), "times the 2010 level"  )    

```

## The code produces this output

```{r, echo=FALSE, eval=TRUE, }
costs <- read.csv("Publisher_Costs_FI_Full_Data.csv")
uni <- "Aalto University"
costs <- filter(costs, Publisher.Supplier == "Elsevier") %>% filter(X...Organization.name == uni)

model.i <- lm(Cost~Year, costs)
    y <- predict(model.i, data.frame(Year = 2050))
    #add prediction to values
    yearlyCosts <- c(costs$Cost, y)
    #create vector to color the predicted bar differently 
    colours <- c(rep("gray", length(costs$Cost)), "red")
    #Create plot
    barplot(yearlyCosts, names.arg = c(costs$Year, 2050) , col = colours, xlab = "Year", ylab="Subscription Cost (EUR)")

    z <- y/costs$Cost[1]
      paste(uni, "will pay", signif(y, digits = 4), "EUR at",2050, ".", "This is", round(z, digits=2), "times the 2010 level"  )    

```




